\section{Conclusion}\label{sec:conclusion}
Attitude determination is a vital part of all spacecraft missions.
Previously, devices such as magnetometers and Sun sensors would give one observation each in both the body and inertial
frames.
The advantage of star trackers is the presentation of multiple observations with just one device.
Star identification is the process associated that maps observations found in the body frame (i.e.\ the image) to the
inertial frame (i.e.\ the catalog).

Gottlieb's Angle method, Liebe's Dot Angle method, Motari's Pyramid method, Cole and Crassidis's Spherical and
Planar Triangle method, and Toloei's Composite Pyramid method were adjusted to fit a general identification flow
and were analyzed in terms of their query, reduction, and identification steps.
Portions that were interchangeable amongst all methods such as database access and centroid determination were
normalized or removed to focus on the star identification aspect itself.

In all experiments, the Pyramid method ranked first (or close to first) in running time and fairly high in accuracy.
The average short running time is a result of a relatively fast query step, and its accuracy can be attributed to the
verification procedure at identification time.
The Pyramid method is the least sensitive to hyperparameter changes in terms of query size response and accuracy
response.
This method produced the lowest number of catalog candidate sets for a given query, and is the most tolerant of
both Gaussian noise and false stars.

The Angle method had the fastest query step, which stems from the small catalog ($\sim$35 times smaller than
the next larger catalogs, the triangle catalogs).
There were a few instances where the accuracy of the Angle method was greater than the Pyramid method, but this came
at the cost of runtime.
The results produced by the query step heavily impacted the reduction and identification runtime.
For the no noise end-to-end case, this method was a factor of MP200 times slower than the next slowest method (Dot
Angle method).

The Dot Angle method is the most sensitive to hyperparameter changes, but had a larger ideal region than the other
methods.
The catalog for this method was $\sim$105 times larger than the Angle method, and consequently had the longest query
step.
This method handles Gaussian noise the best of all other methods, being the second fastest to identify an image and
being first in how accurate the result is.
In terms of false stars, this method ranks last in accuracy.

The accuracy of the Spherical and Planar Triangle methods rank in between for both Gaussian noise and false stars.
These methods produced the smallest amount of candidates on average, meaning that the reduction filter did not have to
resort to 
%largest catalogs (Spherical and Planar Triangle).
%A smaller catalog means that the search will be faster.



%Despite having the largest catalog (~105 times larger than the Angle/Pyramid catalog), the time to query is actually
%faster than that of the Spherical and Planar Triangle methods.
%This method also has a smaller time complexity than the triangle methods, placing its running time between the fast
%Pyramid/Angle methods and slow triangle methods.
%The accuracy of this method is higher than the Angle method, but is not as tolerant to various noise as the Pyramid
%method is.
%
%The Spherical and Planar Triangle methods were always 4th and 5th in running time, and roughly tied for accuracy
%with the Dot Angle method.
%Catalog queries involving triangular features were measured to be 100 times slower than the the Pyramid/Angle methods.
%This is a heavy performance hit.
%Despite the pivoting reduction process to reduce the number of queries, these methods were always slower than
%their angular feature counterparts.
%
%This pivoting process is essential to reducing the running time of the triangle methods, which is why the Composite
%Pyramid is the least accurate and slowest of all the methods tested here.
%Given a slow query time, an overly aggressive $\{ R \mid 1 = |R| \}$ reduction filter instead of the pivoting process,
%and an additional filter in \Call{CompositeVerify}{}, this method is not efficient with its queries.
%
%Overall, the Pyramid method is the most accurate under various noise and produces a result the fastest.
%If one is working with a small field-of-view with limited stars to choose from, then the Dot Angle method would be
%the next logical choice for retaining accuracy.
%If speed is a factor as well, then the Angle method should suffice.